\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
moved osm critique and tweaking sumo prgrph

% TODO better name!
\title{\LARGE \bf
Approximately Orchestrated Routing and Transportation Analyzer:\\
Large-scale Traffic Simulation for Autonomous Vehicles
}

@@

% TODO theme: easy simulation in your city, in 2 minutes!

% In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
% Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2007, six of the competing teams completed the 96km course set for the DARPA
Urban Challenge \cite{spectrumUrbanChallenge2007}. They did so while
obeying the traffic laws followed by human drivers, navigating along with other
moving vehicles, and following correct intersection precedence order. Since
then, Google's driverless cars have clocked more than 250,000km on public roads
in urban California, USA \cite{tedThrun2011}. In 2010, researchers from the
University of Parma successfully completed an autonomous
\textit{intercontinental} run from Parma, Italy to Shanghai, China
\cite{cnnVislab2010}. The successful completion of all these milestones
suggests that autonomous cars are here to stay, and are ever closer to becoming
commercially available. With the arrival of autonomous cars, it also becomes
possible to optimize traffic in ways not possible for human drivers. 
%\commentd{If we need space, I agree with Dr Chiu, some of this could be
%trimmed}

@@

\begin{figure}[t]
  \centering \includegraphics[width=0.9\linewidth]{downtown_atx.png}
  \caption{A simulation of autonomous agents in downtown Austin, Texas, as visualized through the UI available within the AORTA simulator}
  \label{fig:ui_screenshot}
  \vspace{-20pt}
\end{figure}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}, a platform designed for testing autonomous vehicle
behaviors and intersection policies. Autonomous vehicles, termed agents, use
behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. Intersection policies
deisgnate when it is safe for an agent to cross an intersection.  AORTA's goal
is to allow for the definition of new agent behaviors and intersection policies
to optimize autonomous traffic. Additionally, by assigning human-like behaviors
such as the ``car following model'' \cite{brackstone1999car} to agents, and
traffic-signal-like policies to intersections, AORTA could potentially simulate
human traffic.

% AORTA allows for the creation of
% intersection policies that designate when agents can cross the intersection.

@@

This paper explores the state-of-the-art in traffic simulators in section
\ref{sec:related_work}, followed by a description of AORTA's architecture in
section \ref{sec:arch}.  Use of OSM data in AORTA is explained in section
\ref{sec:map}, along with a description of the simulator in section
\ref{sec:simulation}. A simple experiment is presented in section
\ref{sec:results} demonstrating an application built on top of AORTA, that
evaluates different intersection policies in a large scale scenario. The paper
then concludes with a discussion on future work.

@@

% just draw differences between us and them

@@

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to improve these plans by attempting to
minimize the total amount of time by which individuals are late to their
destinations. This goal is somewhat different from that of AORTA, where the
routes (demand) supplied by individuals is taken as is, and each agent has a
specified destination at a given point in time. Instead, AORTA focuses on
vehicle behaviors and intersection policies that can help this agent reach its
destination faster.

% This goal is somewhat different from that of AORTA, where the
% routes (demand) supplied by individuals is taken as is and does not have a
% pre-determined ideal time of arrival. Rather than improving agent routes, AORTA
% allows creating entirely different behaviors for both vehicles and
% intersections in order to simulate a different environment instead of
% optimizing plans for a society in a static environment \commentpk{I think MIke
% made these changes last night, but I am not sure if the last few sentences are
% clear to me}.

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares many similar goals with AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency.  AORTA and SUMO differ in the manner in which
intersections are handled. SUMO uses traditional traffic signals, while AORTA
allows intersections to grant agents entry by any general policy. These policies
can use traditional schemes such as traffic signals or stop-sign based
precedence, or more efficient methods designed specifically for autonomous
vehicles \cite{JAIR08-dresner}.
\commentd{Are we sure SUMO is not easily configurable in this way?}

@@

@@

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. There are many circumstances where AORTA
simulates one intersection as several in close proximity because roads do not
geometrically line up, but functionally they do.  If OSM encoded this data, the
performance of intersection policies and the realism of the simulation would
improve. Other simulators have identified similar issues before
\cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

>>>>

\title{\LARGE \bf
Approximately Orchestrated Routing and Transportation Analyzer:\\
Large-scale Traffic Simulation for Autonomous Vehicles
}

@@

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2007, six of the competing teams completed the 96km course set for the DARPA
Urban Challenge \cite{spectrumUrbanChallenge2007}. They did so while
obeying the traffic laws followed by human drivers, navigating along with other
moving vehicles, and following correct intersection precedence order. Since
then, Google's driverless cars have clocked more than 250,000km on public roads
in urban California, USA \cite{tedThrun2011}. In 2010, researchers from the
University of Parma successfully completed an autonomous
\textit{intercontinental} run from Parma, Italy to Shanghai, China
\cite{cnnVislab2010}. The successful completion of all these milestones
suggests that autonomous cars are here to stay, and are ever closer to becoming
commercially available. With the arrival of autonomous cars, it also becomes
possible to optimize traffic in ways not possible for human drivers.

@@

\begin{figure}[t]
  \centering \includegraphics[width=0.9\linewidth]{downtown_atx.png}
  \caption{Visualizing autonomous agents in downtown Austin, Texas, with AORTA's UI}
  \label{fig:ui_screenshot}
  \vspace{-20pt}
\end{figure}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}. AORTA is a platform designed for testing autonomous
vehicle behaviors and intersection policies. Autonomous vehicles, termed agents,
use behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. Intersection policies deisgnate
when it is safe for an agent to cross an intersection.  AORTA's goal is to allow
for the definition of new agent behaviors and intersection policies to optimize
autonomous traffic. Additionally, by assigning human-like behaviors such as the
``car following model'' \cite{brackstone1999car} to agents, and
traffic-signal-like policies to intersections, AORTA could potentially simulate
human traffic.

@@

This paper explores the state-of-the-art in traffic simulators in section
\ref{sec:related_work}, followed by a description of AORTA's architecture in
section \ref{sec:arch}.  Use of OSM data in AORTA is explained in section
\ref{sec:map}, along with a description of the simulator in section
\ref{sec:simulation}. Section \ref{sec:results} demonstrates an application
built on top of AORTA and presents a simple experiment evaluating different
intersection policies in a large scale scenario. The paper then concludes with a
discussion on future work.

@@

@@

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to improve these plans by attempting to
minimize the total amount of time by which individuals are late to their
destinations. This goal is somewhat different from that of AORTA, where the
routes (demand) supplied by individuals is taken as is.  Instead, AORTA focuses
on vehicle behaviors and intersection policies that can help this agent reach
its destination faster.

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares many similar goals with AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency. While SUMO has a flexible system for managing
traditional traffic signals, AORTA's general intersection policies are designed
with autonomous vehicles in mind. These policies can use traditional schemes
such as traffic signals or stop-sign based precedence, or more efficient methods
designed specifically for autonomous vehicles \cite{JAIR08-dresner}. In
addition, AORTA's core implementation, written in Scala \cite{scala}, differs
from that of SUMO, written in C++, in that it uses a higher-level language.

@@

\subsection{Limitations with OSM}

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. There are many circumstances where AORTA
simulates one intersection as several in close proximity because roads do not
geometrically line up, but functionally they do. If OSM encoded this data, the
the realism of the simulation would improve. Other simulators have identified
similar issues before \cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

@@
